Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
Added time spent not hashing discussion

@@

We have not use the fastest available implementations for all of the
candidates, we also know that our bindings creates an overhead for all calls.
Therefore we have tried to calculate the results that could have been achieved
in Tahoe-\ac{LAFS} if we had managed to obtain the speeds of the fastest
implementations in \ac{SUPERCOP}. The results can be seen in
\autoref{appendix:optimzed_sha3}.

% Describe inconsistencies in the numbers, and try to explain them.
% Time spent not hashing varies because: Variable use of CPU regs?
%
% Compare our results with general (SUPERCOP) results.
%
% How much gain can Tahoe-LAFS get by switching to SHA-3?
%
% Drag in the five selected remaining candidates.

@@

The Python-bindings generated for Cython in C are not necessarily the most
optimized versions possible to write and they are ugly to read or change (from
a C perspective). However we consider them to be good enough, and they are
equal for all the \ac{SHA}-3 candidates which means they should give the same
performance penalty. The \ac{SHA}-256 version will of course not suffer from
the same penalty, however we believe the possible performance gain is small.
This is due to the fact that no intensive operations take place in our
Cython-code. However we do believe that our bindings are affected by the

>>>>

\subsection{Time spent not hashing} A strange part of our result is that the
time Tahoe-\ac{LAFS} spends not callign the hash function is not static for all
candidates, which we expected.  The results of how much this deviance is
varies, although it looks to be bounded by some limits that are not the same
for all candidates. This leads us to believe that the hash function is to
blame, with noise from the system probably being the cause of the variation.
The time is recorded right before and right after the calls to our bindings,
which means that if the implementations are to be blamed they have to do
something to the system which delays later Tahoe-{LAFS} operations. We only
speculate in what they are changing and doing differently, but we suspect the
amount of registers and how much memory and cache the implementation uses as
probable causes.

@@

We have not use the fastest available implementations for all of the
candidates, we also know that our bindings creates an overhead for all calls.
Therefore we have tried to calculate the results that could have been achieved
in Tahoe-\ac{LAFS} if we had managed to obtain the speeds of the fastest
implementations in \ac{SUPERCOP}. The results can be seen in
\autoref{appendix:optimized_sha3}.

% Describe inconsistencies in the numbers, and try to explain them.
% Time spent not hashing varies because: Variable use of CPU regs?
%
% Compare our results with general (SUPERCOP) results.
%
% How much gain can Tahoe-LAFS get by switching to SHA-3?

@@

The Python-bindings generated for Cython in C are not necessarily the most
optimized versions possible to write and they are ugly to read and change (from
a C perspective). However they are equal for all the \ac{SHA}-3 candidates
which means they should give the same performance penalty. The \ac{SHA}-256
version will of course not suffer from the same penalty. From
\autoref{tbl:cython:overhead} we can see the performance penalty of our
bindings, and we do believe better bindings can be made, also with the use of
Cython, but by someone with more skill and knowledge than us.
